To run with the hare and hunt with the hounds: Optimal recommendation system with competing sellers. \\ Master Thesis

### 2020-04-03 Thesis.tex
Add files via upload
Thesis

\documentclass[a4paper]{article}
\usepackage[12pt]{extsizes} % 
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage{setspace,amsmath}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage{titlesec}
%\usepackage{harvard}
\usepackage[round]{natbib}
\usepackage{pdfpages}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{angles,quotes}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{breakcites}
\interfootnotelinepenalty=10000
\usepackage[makeroom]{cancel}
\usepackage{mathrsfs} % 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\addto\captionsrussian{\renewcommand{\figurename}{Fig.}}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{}
{\hbox{$\mathsurround=0pt #1$}}{}}
\usepackage{graphicx}  % 
\graphicspath{{images/}{images2/}}  % 
\setlength\fboxsep{3pt} %  \fbox{} 
\setlength\fboxrule{1pt} % \fbox{}
\usepackage{wrapfig} % 
%\newenvironment{abstract}[0]{\small\rm
%	\begin{center}ABSTRACT
%		\\ \vspace{8pt}
%		\begin{minipage}{5.2in}\smalllineskip
%			\hspace{1pc}}{\end{minipage}\end{center}\vspace{-1pt}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\norma}{\mathcal{N}}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\summa}{\sum_{i=1}^n}
\usepackage[left=25mm, top=20mm, right=25mm, bottom=20mm, nohead, footskip=10mm]{geometry} % 
\usepackage{tikz} % 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{definition}[theorem]{Definition}
%\let\cite = \citeasnoun
\title{To run with the hare and hunt with the hounds: Optimal recommendation system with competing sellers. \\ Master Thesis}
\date{}
\author{Danil Fedchenko}
\begin{document} % 
	\maketitle
	\begin{abstract}
		Many e-commerce platforms that connect buyers and sellers employ recommender systems to help customers find products and services. These systems may have several potential effects on strategies of competing sellers: on one hand, more people become aware of products, so sellers may sell more goods and benefit from the presence of the recommender system. On the other hand, at the same time, more people become aware of the competitor seller. The latter effect may intensify the price competition and may hurt sellers but, of course, benefit customers. However, many platforms charge firms for sales and as a result have the stakes in firms profits. Thus, by designing the recommender policy the platform should balance the pro-competitive care about customers and anti-competitive incentives to keep high prices. The main goal of this work is to study this trade-off in details. I am solving for an optimal recommender policy and investigate factors that may affect it.
	\end{abstract}
\newpage
	\section{Introduction}
	\section{Literature review}
	\section{Model}
	The model I consider is similar to that considered by \cite{levin2009quality}, the difference is that I introduce a new player -- a platform which employs a recommender system (I will use words ``platform'' and ``recommender system'' interchangeably).

@@

	\begin{lemma}\label{without}
		If qualities $q_A$ and $q_B$ are observable then the demand for each good and equilibrium prices are defined as follows:
		\begin{align*}
		D_i = x_0 &= \frac{1}{2} - \frac{p_i - p_{-i}}{2} + \frac{q_i-q_{-i}}{2}\\
		p_i &= 1 + \frac{q_i - q_{-i}}{3}
		\end{align*}
	\end{lemma}
\begin{proof}
	The proof will be completed.
\end{proof}
	The lemma above demonstrates that without the platform the seller with the higher quality sets a higher price, and if seller $i$ decides to undercut the competitor and sets the price $p_{-i} - \varepsilon$ then the gain in additional demand will be $\frac{\varepsilon}{2}$.

@@

	\subsection{Observable qualities. With the platform.}
	For simplicity, I assume firstly that $\alpha$ is fixed.
	\begin{proposition} \label{with}
		If qualities $q_A$ and $q_B$ are observable then the recommender system induces the following demands for each good and equilibrium prices:
		\begin{align*}
		D_A &= \hat{x} = \frac{1}{2} - \frac{\gamma-\alpha}{2 \gamma}(p_A - p_B) + \frac{q_A - q_B}{2}\\
		D_B &= 1 - D_A\\
		p_i &= \frac{\gamma}{\gamma - \alpha} + \frac{\gamma(q_{i} -q_{-i})}{3(\gamma-\alpha)}
		\end{align*}
		and the optimal recommender policy implies:
		\begin{itemize}
			\item recommending the seller $A$ for those customers whose location $x \le \hat{x}$
			\item recommending the seller $B$ otherwise
		\end{itemize}
	\end{proposition}
	\begin{proof}
		The proof will be completed.
	\end{proof}
	Comparing the results of the Proposition \ref{with} with Lemma \ref{without} several things are worth noting. First of all, with the recommender system the term $\frac{p_A-p_B}{2}$ in the expression for demand has an extra multiplier $\frac{\gamma-\alpha}{\gamma} \in (0, 1)$. The latter fact means that is the seller $A$ decides to undercut the competitor and sets a price $p_B - \varepsilon$, with the recommender system the resulting gain in demand will be $\frac{\gamma - \alpha}{\gamma} \frac{\varepsilon}{2}$ which is strictly below $\frac{\varepsilon}{2}$ the result we obtained for the case without the platform. That means that now the sellers have fewer incentives to undercut the competitor, i.e. the presence of recommender system which has stakes in sellers' profits softens competition. As a result, the equilibrium prices a higher. The picture below (Fig. \ref{fig1}) demonstrates graphically the impact of the recommender system.

@@

	The optimal platform's policy can be found separately: firstly the platform may obtain the optimal recommendation (as a function of $\alpha$) treating the commission rate $\alpha$ as given, and then find an optimal commission rate. The next proposition characterize the optimal recommendation strategy given the commission rate $\alpha$.
	\begin{proposition}\label{precise}
		Given $\alpha$, the optimal recommender policy is given by $$\hat{x} = \frac{1}{2} - \frac{\gamma-\alpha}{2 \gamma}(p_A - p_B) + \frac{\tilde{q}_A - \tilde{q}_B}{2}$$
		Equilibrium prices are $$p_i = \frac{\gamma}{\gamma - \alpha} + \frac{\gamma(\tilde{q}_{i} -\tilde{q}_{-i})}{3(\gamma-\alpha)}$$ where $$\tilde{q}_i = \begin{cases}
		q_i, \text{ if firm }i\text{ discloses }\\
		\frac{q^*}{2}, \text{ otherwise}
		\end{cases}$$
		and
		\begin{align*}
		q^* = -\frac{5}{3} + \frac{1}{3 \gamma} \sqrt{25 \gamma^2 + \frac{216 c \gamma (\gamma - \alpha)}{1 - \alpha}}
		\end{align*}
	\end{proposition} 
\begin{proof}
	Will be completed
\end{proof}
Comparing this result to the optimal recommendation strategy in case of unobservable quality, we note that instead of real qualities, in all formulas are used ``perceived'' qualities i.e. the exact qualities if the firm discloses and the conditional expectation of the quality given the fact that the firm does not disclose. The threshold $q^*$ is found as a quality that renders the seller indifferent between costly disclosure and non-disclosure. The following step would be to find an optimal commission rate $\alpha$ but prior to that let me analyse the equilibrium information disclosure and how the recommender system affects it.
\begin{proposition}\label{thres}
	\begin{enumerate}[(i)]
		\item If $\gamma <1$ then $\frac{\partial q^*}{\partial \alpha} < 0$ i.e. sellers disclose more information if commissions increase
		\item If $\gamma > 1$ then $\frac{\partial q^*}{\partial \alpha} > 0$ i.e. sellers disclose less information if commissions increase
		\item If $\gamma = 1$ then $\frac{\partial q^*}{\partial \alpha} = 0$ i.e. amount of information disclosed does not depend on the commission rate
	\end{enumerate}
\end{proposition}
\begin{proof}
	Proof will be completed.
\end{proof}
The figure below (Fig. \ref{fig2}) demonstrate the threshold $q^*$ as a function of $\alpha$.
	\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{thres}
	\caption{$q^*$ as a function of $\alpha$}\label{fig2}
\end{figure}

@@

Finally, let me summarize the optimal recommender policy by finding an optimal commission rate $\alpha$.
\begin{proposition}\label{opt_alpha}
	\begin{enumerate}[(i)]
		\item If $\gamma < 1$ then $\frac{\partial \pi}{\partial \alpha} > 0$, so the optimal recommendation policy implies the highest commission $\alpha = \bar{\alpha}$
		\item If $\gamma > 1$ then $\frac{\partial \pi}{\partial \alpha} < 0$, so the optimal recommendation policy implies $\alpha = 0$
	\end{enumerate}
\end{proposition}
\begin{proof} Will be completed.
\end{proof}

@@

Formally, I assume that before making recommendation to a particular customer whose true location $x$ is equal to $x_0 \in [0, 1]$ the platform receives a signal $s$ such that $$\mathbb{P}(s=x_0|x=x_0) = \beta \in [0, 1]$$ and with probability $1-\beta$, $s \sim U(0, 1)$. I will refer to $\beta$ as the recommender system precision. In this case, as it is shown by \cite{li2018recommender} the conditional expectation regarding the true location is equal to $$\mathbb{E}[x|s=x_0] = \beta x_0 + \frac{1-\beta}{2}$$
The result above is quite intuitive: the higher is precision the more weight the platform assigns to the signal, while when the precision is low the platform more frequently infers that the signal is not correct and prescribes to the customer an average location $\frac{1}{2}$.

>>>>

\documentclass[a4paper]{article}
\usepackage[12pt]{extsizes} % 
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage{setspace,amsmath}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage{titlesec}
%\usepackage{harvard}
\usepackage[round]{natbib}
\usepackage{pdfpages}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{angles,quotes}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{breakcites}
\interfootnotelinepenalty=10000
\usepackage[makeroom]{cancel}
\usepackage{mathrsfs} % 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\addto\captionsrussian{\renewcommand{\figurename}{Fig.}}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{}
{\hbox{$\mathsurround=0pt #1$}}{}}
\usepackage{graphicx}  % 
\graphicspath{{images/}{images2/}}  % 
\setlength\fboxsep{3pt} %  \fbox{} 
\setlength\fboxrule{1pt} % \fbox{}
\usepackage{wrapfig} % 
%\newenvironment{abstract}[0]{\small\rm
%	\begin{center}ABSTRACT
%		\\ \vspace{8pt}
%		\begin{minipage}{5.2in}\smalllineskip
%			\hspace{1pc}}{\end{minipage}\end{center}\vspace{-1pt}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\norma}{\mathcal{N}}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\summa}{\sum_{i=1}^n}
\usepackage[left=25mm, top=20mm, right=25mm, bottom=20mm, nohead, footskip=10mm]{geometry} % 
\usepackage{tikz} % 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{definition}[theorem]{Definition}
%\let\cite = \citeasnoun
\title{To run with the hare and hunt with the hounds: Optimal recommendation system with competing sellers. \\ Master Thesis}
\date{}
\author{Danil Fedchenko\thanks{I am very grateful to Sergei Izmalkov for his help during the work on this project}}
\begin{document} % 
	\maketitle
	\begin{abstract}
		Many e-commerce platforms that connect buyers and sellers employ recommender systems to help customers find products and services. These systems may have several potential effects on strategies of competing sellers: on one hand, more people become aware of products, so sellers may sell more goods and benefit from the presence of the recommender system. On the other hand, at the same time, more people become aware of the competitor seller. The latter effect may intensify the price competition and may hurt sellers but, of course, benefit customers. However, many platforms charge firms for sales and as a result have the stakes in firms profits. Thus, by designing the recommender policy the platform should balance the pro-competitive care about customers and anti-competitive incentives to keep high prices. The main goal of this work is to study this trade-off in details. I am solving for an optimal recommender policy and investigate factors that may affect it.
	\end{abstract}
\newpage
\tableofcontents
\newpage
	\section{Introduction}
	\section{Literature review}
	\section{Model}
	The model I consider is similar to that considered by \cite{levin2009quality}, the difference is that I introduce a new player -- a platform which employs a recommender system (I will use words ``platform'' and ``recommender system'' interchangeably).

@@

	\begin{lemma}\label{without}
		If qualities $q_A$ and $q_B$ are observable then the demand for each good and equilibrium prices are defined as follows:
		\begin{align*}
		D_A &= x_0 = \frac{1}{2} - \frac{p_A - p_{B}}{2} + \frac{q_A-q_{B}}{2}\\
		D_B &= 1 - D_A\\
		p_i &= 1 + \frac{q_i - q_{-i}}{3}
		\end{align*}
	\end{lemma}
\begin{proof}
	The standard way to solve the Hotelling model is to define a marginal consumer $x_0$ i.e. a consumer who is indifferent between buying from sellers $A$ or $B$. Thus, $x_0$ is determined by the following equation: $$V+q_A-p_A - x_0 = V+q_B - p_B - (1-x_0)$$
	hence $$x_0 = \frac{1}{2} - \frac{p_A - p_B}{2} + \frac{q_A - q_B}{2}$$
	Sellers set prices $p_A, p_B$ simultaneously to solve the following problems:
	$$p_A \cdot x_0 = p_A \left(\frac{1}{2} - \frac{p_A - p_B}{2} + \frac{q_A - q_B}{2}\right) \to \underset{p_A}{\max}$$
	$$p_B \cdot (1-x_0) = p_B \left(\frac{1}{2} + \frac{p_A - p_B}{2} - \frac{q_A - q_B}{2}\right) \to \underset{p_B}{\max}$$
	The system of first order conditions is given by:
	\begin{align*}
	\begin{cases}
	p_A = \frac{1}{2} + \frac{p_B}{2} + \frac{q_A - q_B}{2}\\
	p_B = \frac{1}{2} + \frac{p_A}{2} - \frac{q_A - q_B}{2}
	\end{cases}
	\end{align*}
	Solving the system above yields $p_i = 1 + \frac{q_i - q_{-i}}{3}$
\end{proof}
	The lemma above demonstrates that without the platform the seller with the higher quality sets a higher price, and if seller $i$ decides to undercut the competitor and sets the price $p_{-i} - \varepsilon$ then the gain in additional demand will be $\frac{\varepsilon}{2}$.

@@

	\subsection{Observable qualities. With the platform.}
	For simplicity, I assume firstly that $\alpha$ is fixed.
	\begin{proposition} \label{with}
		If qualities $q_A$ and $q_B$ are observable then the recommender system induces the following demands for each good and equilibrium prices:
		\begin{align*}
		D_A &= \hat{x} = \frac{1}{2} - \frac{\gamma-\alpha}{2 \gamma}(p_A - p_B) + \frac{q_A - q_B}{2}\\
		D_B &= 1 - D_A\\
		p_i &= \frac{\gamma}{\gamma - \alpha} + \frac{\gamma(q_{i} -q_{-i})}{3(\gamma-\alpha)}
		\end{align*}
		and the optimal recommender policy implies:
		\begin{itemize}
			\item recommending the seller $A$ for those customers whose location $x \le \hat{x}$
			\item recommending the seller $B$ otherwise
		\end{itemize}
	\end{proposition}
	\begin{proof}
	 The optimal recommender strategy consists of two functions $r_A(x, p_A, p_B, q_A, q_B)$, $r_B(x, p_A, p_B, q_A, q_B)$ (which for simplicity I will denote as simply $r_A(x), r_B(x)$) which are the probabilities for the customer with location $x$ to be recommended the seller $A$ and $B$ respectively. Clearly these two functions should satisfy $$0 \le r_i(x) \le 1,\ \forall\ i \in \{A, B\},\ \forall\ x \in [0, 1] $$ $$0 \le r_A(x) + r_B(x) \le 1,\ \forall\ x \in [0, 1]$$ 
	 Firstly, let me show that it is not optimal to have $r_A(x) + r_B(x) < 1$ for any $x$. Suppose on the contrary that $\exists\ x \in [0, 1], r_A(x)+r_B(x) < 1$. If for that customer any of expressions $V+q_A-p_A-x$, $V+q_B-p_B-(1-x)$ are positive then the platform can increase the probability of recommendation the seller whose good yields the customer positive utility (if both yields positive the good that yields more). Since the customer derives positive utility, $CS$ increases, this, in turn, increases the platform's objective function, hence $r_A(x) +r_B(x) < 1$ was not optimal. If both expressions $V+q_A-p_A-x$, $V+q_B-p_B-(1-x)$ are negative customer will not follow the recommendation no matter what are $r_A(x), r_B(x)$, so, without loss of generality we can restrict attention only to cases $r_A(x) + r_B(x) = 1$ i.e. to find only $r_A(x)$.

	 The objective of the recommender system is \begin{align*}
	 \int_{0}^1 \alpha p_A r_A(x)dx + \int_{0}^1 \alpha p_B r_B(x)dx + \gamma \biggl( \int_{0}^1 (V+q_A-p_A-x)r_A(x)dx + \\+\int_{0}^1 (V+q_B-p_B-(1-x))r_B(x)dx \biggr) = \int_0^1 (\gamma V + \gamma q_A - (\gamma - \alpha)p_A - \gamma x) r_A(x)dx +\\+ \int_0^1 (\gamma V + \gamma q_B - (\gamma - \alpha)p_B - \gamma(1- x))(1- r_A(x))dx
	 \end{align*}
	 The platform maximizes the above function subject to the constraint $0 \le r_A(x) \le 1,\ \forall\ x \in [0, 1]$. Clearly, the objective function is maximized for $$r_A(x) = \begin{cases}
	 1, \text{if the expression under the first integral is higher}\\
	 0, \text{if the expression under the second integral is higher}
	 \end{cases}$$
	 That is, the seller $A$ is recommended to customers whose locations are to the left of $$\hat{x} = \frac{1}{2} - \frac{\gamma - \alpha}{\gamma} \frac{p_A - p_B}{2} + \frac{q_A - q_B}{2}$$
	 and the seller $B$ is recommended otherwise.

	 Given the demand, 	sellers set prices $p_A, p_B$ simultaneously to solve the following problems:
	 $$(1-\alpha)\cdot p_A \cdot \hat{x} = p_A \left(\frac{1}{2} - \frac{\gamma - \alpha}{\gamma} \frac{p_A - p_B}{2} + \frac{q_A - q_B}{2}\right) \to \underset{p_A}{\max}$$
	 $$(1-\alpha)\cdot p_B \cdot (1-\hat{x}) = p_B \left(\frac{1}{2} + \frac{\gamma - \alpha}{\gamma} \frac{p_A - p_B}{2} - \frac{q_A - q_B}{2}\right) \to \underset{p_B}{\max}$$
	 The system of first order conditions is given by:
	 \begin{align*}
	 \begin{cases}
	 p_A = \frac{\gamma}{2(\gamma - \alpha)} + \frac{p_B}{2} + \frac{\gamma(q_A - q_B)}{2(\gamma - \alpha)}\\
	 p_B = \frac{\gamma}{2(\gamma - \alpha)} + \frac{p_A}{2} - \frac{\gamma(q_A - q_B)}{2(\gamma - \alpha)}
	 \end{cases}
	 \end{align*}
	 Solving the system above yields $p_i = \frac{\gamma}{\gamma - \alpha} + \frac{\gamma(q_i - q_{-i})}{3(\gamma - \alpha)}$
	\end{proof}
	Comparing the results of the Proposition \ref{with} with Lemma \ref{without} several things are worth noting. First of all, with the recommender system the term $\frac{p_A-p_B}{2}$ in the expression for demand has an extra multiplier $\frac{\gamma-\alpha}{\gamma} \in (0, 1)$. The latter fact means that is the seller $A$ decides to undercut the competitor and sets a price $p_B - \varepsilon$, with the recommender system the resulting gain in demand will be $\frac{\gamma - \alpha}{\gamma} \frac{\varepsilon}{2}$ which is strictly below $\frac{\varepsilon}{2}$ the result we obtained for the case without the platform. That means that now the sellers have fewer incentives to undercut the competitor, i.e. the presence of recommender system which has stakes in sellers' profits softens competition. As a result, the equilibrium prices a higher. The picture below (Fig. \ref{fig1}) demonstrates graphically the impact of the recommender system.

@@

	The optimal platform's policy can be found separately: firstly the platform may obtain the optimal recommendation (as a function of $\alpha$) treating the commission rate $\alpha$ as given, and then find an optimal commission rate. The next proposition characterize the optimal recommendation strategy given the commission rate $\alpha$.
	\begin{proposition}\label{precise}
		Given $\alpha$, the optimal recommender policy is given by $$\hat{x} = \frac{1}{2} - \frac{\gamma-\alpha}{2 \gamma}(p_A - p_B) + \frac{\tilde{q}_A - \tilde{q}_B}{2}$$
		Equilibrium prices are $$p_i = \frac{\gamma}{\gamma - \alpha} + \frac{\gamma(\tilde{q}_{i} -\tilde{q}_{-i})}{3(\gamma-\alpha)}$$ where $$\tilde{q}_i = \begin{cases}
		q_i, \text{ if firm }i\text{ discloses }\\
		\frac{q^*}{2}, \text{ otherwise}
		\end{cases}$$
		and
		\begin{align}\label{threshold}
		q^* = -\frac{5}{3} + \frac{1}{3 \gamma} \sqrt{25 \gamma^2 + \frac{216 c \gamma (\gamma - \alpha)}{1 - \alpha}}
		\end{align}
	\end{proposition} 
\begin{proof}
	From the Bayes rule it follows that if the seller does not disclose the information the platform forms beliefs that the quality is $\frac{q^*}{2}$. Given the platform's beliefs regarding the quality, the proof exactly repeats that of Proposition \ref{with}. It remains to find $q^*$. This threshold is found as the minimal quality that renders the seller indifferent between disclosing and not disclosing the information. That is, $q^*$ is determined as a solution to the following equation:
	\begin{align*}
	\mathbb{E} [\pi_i|q_i=q^*, \text{disclose}] - c = \mathbb{E} [\pi_i|q_i=q^*, \text{do not disclose}]
	\end{align*}
	\begin{align*}
	&(1-\alpha)\int_{0}^{q^*} \left(\frac{\gamma}{\gamma - \alpha} + \frac{\gamma\left(q^* - \frac{q^*}{2}\right)}{3(\gamma - \alpha)} \right) \left(\frac{1}{2} - \frac{q^* - \frac{q^*}{2}}{6}\right)dq_B +\\ &+(1-\alpha)\int_{q^*}^{1} \left(\frac{\gamma}{\gamma - \alpha} + \frac{\gamma(q^* - q_B)}{3(\gamma - \alpha)} \right) \left(\frac{1}{2} - \frac{q^* - q_B}{6}\right)dq_B - c = \\
	&=(1-\alpha)\int_{0}^{q^*} \left(\frac{\gamma}{\gamma - \alpha} + \frac{\gamma\left(\frac{q^*}{2} - \frac{q^*}{2}\right)}{3(\gamma - \alpha)} \right) \left(\frac{1}{2} - \frac{\frac{q^*}{2} - \frac{q^*}{2}}{6}\right)dq_B +\\
	&+ (1-\alpha)\int_{q^*}^{1} \left(\frac{\gamma}{\gamma - \alpha} + \frac{\gamma(\frac{q^*}{2} - q_B)}{3(\gamma - \alpha)} \right) \left(\frac{1}{2} - \frac{\frac{q^*}{2} - q_B}{6}\right)dq_B
	\end{align*}
	Solving the equation above yields
	$$q^* = -\frac{5}{3} + \frac{1}{3 \gamma} \sqrt{25 \gamma^2 + \frac{216 c \gamma (\gamma - \alpha)}{1 - \alpha}}$$
\end{proof}
Comparing this result to the optimal recommendation strategy in case of unobservable quality, we note that instead of real qualities, in all formulas are used ``perceived'' qualities i.e. the exact qualities if the firm discloses and the conditional expectation of the quality given the fact that the firm does not disclose. The threshold $q^*$ is found as a quality that renders the seller indifferent between costly disclosure and non-disclosure. The following step would be to find an optimal commission rate $\alpha$ but prior to that let me analyse the equilibrium information disclosure and how the recommender system affects it.
\begin{proposition}\label{thres}
	\begin{enumerate}[(i)]
		\item If $\gamma <1$ then $\frac{\partial q^*}{\partial \alpha} < 0$ i.e. sellers disclose more information if commissions increase
		\item If $\gamma > 1$ then $\frac{\partial q^*}{\partial \alpha} > 0$ i.e. sellers disclose less information if commissions increase
		\item If $\gamma = 1$ then $\frac{\partial q^*}{\partial \alpha} = 0$ i.e. amount of information disclosed does not depend on the commission rate
	\end{enumerate}
\end{proposition}
\begin{proof}
	The proof is straightforward, differentiating \eqref{threshold} with respect to $\alpha$, one can get:
	\begin{align*}
	\frac{\partial q^*}{\partial \alpha} = - \frac{36 c (1-\gamma)}{\sqrt{25 \gamma^2 + \frac{216 c \gamma (\gamma - \alpha)}{1 - \alpha}}} 
	\end{align*}
	which immediately implies the result.
\end{proof}
The figure below (Fig. \ref{fig2}) demonstrate the threshold $q^*$ as a function of $\alpha$.
	\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{thres}
	\caption{$q^*$ as a function of $\alpha$}\label{fig2}
\end{figure}

@@

Finally, let me summarize the optimal recommender policy by finding an optimal commission rate $\alpha$.
\begin{proposition}\label{opt_alpha}
	\begin{enumerate}[(i)]
		\item If $\gamma < 1$ then $\frac{\partial \pi}{\partial \alpha} > 0$, so the optimal recommendation policy implies the highest commission $\alpha = \bar{\alpha}$
		\item If $\gamma > 1$ then $\frac{\partial \pi}{\partial \alpha} < 0$, so the optimal recommendation policy implies $\alpha = 0$
	\end{enumerate}
\end{proposition}
\begin{proof} Given prices $p_A, p_B$ and qualities $q_A, q_B$, total benefit of the platform is equal to:
	\begin{align*}
	\alpha(p_A \hat{x} + p_B(1-\hat{x})) + \gamma \left(\int_{0}^{\hat{x}} (V + q_A - p_A - x)dx + \int_{\hat{x}}^1 (V + q_B - p_B -(1-x))dx\right) = \\
	= 	\alpha(p_A \hat{x} + p_B(1-\hat{x})) + \gamma \left(V - \frac{1}{2}+(1-\hat{x})(q_B - p_B) + \hat{x}(q_A-p_A) - \hat{x}^2  \right)
	\end{align*}
	Where $\hat{x}$ is defined according to Proposition \ref{precise}. Hence, expected total benefit of the platform is
	\begin{align*}
	&\pi = \int_{0}^{q^*} \int_0^{q^*} \biggl( \frac{\alpha \gamma}{\gamma - \alpha} + \gamma \left(V - \frac{3}{4}+ \frac{q^*}{2} - \frac{\gamma}{\gamma - \alpha} \right)\biggr) dq_A dq_B +\\+
	 &\int_0^{q^*} \int_{q^*}^1 \biggl[ \alpha \biggl( \left( \frac{\gamma}{\gamma - \alpha} + \frac{\gamma\left( \frac{q^*}{2} - q_B \right) }{3(\gamma - \alpha)} \right)\left(\frac{1}{2} + \frac{\frac{q^*}{2} - q_B}{6} \right) + \left( \frac{\gamma}{\gamma - \alpha} - \frac{\gamma\left( \frac{q^*}{2} - q_B \right) }{3(\gamma - \alpha)} \right)\left(\frac{1}{2} - \frac{\frac{q^*}{2} - q_B}{6} \right) \biggr)+\\
	 &+\gamma \biggl(V - \frac{1}{2} + \left(\frac{1}{2} - \frac{\frac{q^*}{2} - q_B}{6} \right) \left( q_B - \frac{\gamma}{\gamma - \alpha} + \frac{\gamma \left( \frac{q^*}{2} - q_B \right)}{3 (\gamma - \alpha)} \right)  + \\
	 &+ \left(\frac{1}{2} + \frac{\frac{q^*}{2} - q_B}{6} \right) \left(\frac{q^*}{2} - \frac{\gamma}{\gamma - \alpha} - \frac{\gamma \left( \frac{q^*}{2} - q_B \right)}{3(\gamma - \alpha)} \right)  - \left( \frac{1}{2} + \frac{\frac{q^*}{2} - q_B}{6} \right)^2 \biggr)  \biggr] dq_A dq_B +\\
	 +
	 &\int_{q^*}^{1} \int_{0}^{q^*} \biggl[ \alpha \biggl( \left( \frac{\gamma}{\gamma - \alpha} + \frac{\gamma\left(q_A - \frac{q^*}{2} \right) }{3(\gamma - \alpha)} \right)\left(\frac{1}{2} + \frac{q_A - \frac{q^*}{2}}{6} \right) + \left( \frac{\gamma}{\gamma - \alpha} - \frac{\gamma\left(q_A- \frac{q^*}{2} \right) }{3(\gamma - \alpha)} \right)\left(\frac{1}{2} - \frac{q_A -\frac{q^*}{2}}{6} \right) \biggr)+\\
	 &+\gamma \biggl(V - \frac{1}{2} + \left(\frac{1}{2} - \frac{q_A-\frac{q^*}{2}}{6} \right) \left( \frac{q^*}{2} - \frac{\gamma}{\gamma - \alpha} + \frac{\gamma \left(q_A -  \frac{q^*}{2} \right)}{3 (\gamma - \alpha)} \right)  + \\
	 &+ \left(\frac{1}{2} + \frac{q_A-\frac{q^*}{2}}{6} \right) \left(q_A - \frac{\gamma}{\gamma - \alpha} - \frac{\gamma \left(q_A- \frac{q^*}{2} \right)}{3(\gamma - \alpha)} \right)  - \left( \frac{1}{2} + \frac{q_A - \frac{q^*}{2}}{6} \right)^2 \biggr)  \biggr] dq_A dq_B + \\
	 +
	  &\int_{q^*}^{1} \int_{q^*}^{1} \biggl[ \alpha \biggl( \left( \frac{\gamma}{\gamma - \alpha} + \frac{\gamma\left(q_A - q_B \right) }{3(\gamma - \alpha)} \right)\left(\frac{1}{2} + \frac{q_A - q_B}{6} \right) + \left( \frac{\gamma}{\gamma - \alpha} - \frac{\gamma\left(q_A- q_B \right) }{3(\gamma - \alpha)} \right)\left(\frac{1}{2} - \frac{q_A -q_B}{6} \right) \biggr)+\\
	 &+\gamma \biggl(V - \frac{1}{2} + \left(\frac{1}{2} - \frac{q_A-q_B}{6} \right) \left( q_B - \frac{\gamma}{\gamma - \alpha} + \frac{\gamma \left(q_A -  q_B \right)}{3 (\gamma - \alpha)} \right)  + \\
	 &+ \left(\frac{1}{2} + \frac{q_A-q_B}{6} \right) \left(q_A - \frac{\gamma}{\gamma - \alpha} - \frac{\gamma \left(q_A- q_B \right)}{3(\gamma - \alpha)} \right)  - \left( \frac{1}{2} + \frac{q_A - q_B}{6} \right)^2 \biggr)  \biggr] dq_A dq_B = \\
	 & = \frac{\gamma(216 V - q^{*3} - 161)}{216}
	\end{align*}
	Thus $$\frac{\partial \pi}{\partial \alpha} = -\frac{3 \gamma q^{*2}}{216} \frac{\partial q^*}{\partial \alpha}$$ and using the result of the Proposition \ref{thres} one may finally prove the result.
\end{proof}

@@

Formally, I assume that before making recommendation to a particular customer whose true location $x$ is equal to $x_0 \in [0, 1]$ the platform receives a signal $s$ such that $$\mathbb{P}(s=x_0|x=x_0) = \beta \in [0, 1]$$ and with probability $1-\beta$, $s \sim U(0, 1)$. I will refer to $\beta$ as the recommender system precision. In this case, as it is shown by \cite{li2018recommender} the conditional expectation regarding the true location is equal to \begin{align}\label{signal}
\mathbb{E}[x|s=x_0] = \beta x_0 + \frac{1-\beta}{2}
\end{align}
The result above is quite intuitive: the higher is precision the more weight the platform assigns to the signal, while when the precision is low the platform more frequently infers that the signal is not correct and prescribes to the customer an average location $\frac{1}{2}$.
